\raggedright
% Intro
I am a software engineer with prior experience at Microsoft and the University of California, Irvine. I am interested in the member of technical staff roles at {\company}. I am an excellent choice for these positions. 

% Why company?
Having worked at Microsoft earlier, I reminisce about its inspiring atmosphere. 
I admire Microsoft AI’s mission to build systems that have true artificial
intelligence. I understand how vital data systems are to build
a high quality LLM and would love to participate in advancing Microsoft AI’s systems. With my technical background in robust, efficient systems, I would be a great addition to your team.

% Why me?
My skills and experience, in engineering and research, make me a great candidate. 
At Microsoft Ads, I rebuilt pipeline infrastructure used for the ETL of 100+ data workflows, cutting deployment time from 60 min to < 3 sec. 
I designed a Spark streaming POC to be 3x faster than the corresponding batched pipeline.
I worked with cross-\-geography teams, building data-\-serving API frameworks to run on Azure. 

At UC Irvine, I designed a system to 
preprocess data deemed relevant by an AI- based workflow 
prediction model, trading off query latency with resource usage. 
I collaborated in cross-functional teams with IoT \& civil engineers, chemists on APIs and metric dashboards to monitor drone data from a prescribed burn scenario. 
% At UC Irvine, I built a plugin to integrate simulators into the database. 
% It derived invocation details from the query and suggested parameters for slice-and-dice, abstracting the simulator from the user. 

% Outro
Thank you for reading my letter. I look forward to the opportunity to discuss how my experience and skills can contribute to {\company}.
