% Intro
I am a computer science enthusiast with prior experience at Microsoft and the University of California, Irvine. I am interested in the scientist roles at {\company}. I am a well-suited choice for this position. 

% Why company?
I am impressed by {\company}'s approach to building safe and secure AI. 
Cutting-edge research in large-scale systems to make worldwide impact is exactly the kind of work I am interested in.
With my deep technical background in reliable, efficient systems, I would be a great addition to your team. 

% Why me? 
My skills and experience, in both engineering and research, make me an ideal candidate for this role. 
For example, at Microsoft I built a workflow manager that ran 100+ pipelines, processing petabytes of data per hour. 
I also constructed a proof-of-concept 
Spark Streaming pipeline to compute evaluation data that ran in $1/3$ time of the existing batched method.
This POC introduced Spark to my team, who use it till date.

At UC Irvine, my work in pre-processing data relevant to future queries involved significant research into state-of-the-art compute systems. 
This involved creating a formal dataflow model to help obtain an optimisation problem. 
It quantified the valuable tradeoff between total amount of compute, its allocation 
between regular processing and pre-processing, and end-user latency. 

% Outro
Thank you for reading my letter. I look forward to the opportunity to discuss how my experience and skills can contribute to {\company}.