% ============================================================%
I am writing to express my strong interest in joining {\fullcompany} as a software engineer. 
With my background in software development and research, and passion for creating efficient and resilient systems, I would be a valuable asset to your team.

I find the opportunity at {\company} to work at the intersection of machine learning, search, data and product teams alluring. 
I am particularly drawn to {\company}'s {\product}. {\company}'s commitment to creativity and innovation aligns perfectly with my drive to learn. 
This opportunity is enticing to me due to {\company}'s proactive approach to finding attack vectors. 
I relish the challenge of ensuring that key insights are delivered as fast and reliably as required by {\company}'s standards. 

Working in a data platform team at Microsoft has given me clear insight of the {\myindustryname} industry and I have honed my skills in system design. 
I have learnt the importance of well-structured, modular code. 
At UC Irvine, I improved my ability to independently approach under-specified problems. 
My research on autonomous preprocessing included data management systems that can adapt to improve query processing. 

My experience has familiarized me with {\myindustryname}, which need innovative, efficient design.
Therefore, I have a firm grasp of the core concepts in {\myindustryname} using which today's frameworks are built.
My strong problem-solving skills, technical knowledge and effective collaboration make me an ideal candidate for this position.

\vspace{3mm}
Thank you for considering my application. I am excited to have the opportunity to contribute to {\company}. I would appreciate the opportunity to discuss how my qualifications align with your needs in more detail. 
% Please feel free to contact me at your convenience.