\newcommand{\makework}[6]{
    \expandafter\def\csname work#1\endcsname{#2}
    \expandafter\def\csname title#1\endcsname{#3}
    \expandafter\def\csname time#1\endcsname{#4}
    \expandafter\def\csname place#1\endcsname{#5}
    \expandafter\def\csname detail#1\endcsname{#6}
}

\makework{dremio}
    {Dremio}
    {Software Engineer - PhD Intern}
    {Jun 2022 - Sep 2022}
    {Remote, CA}
    {
    \begin{itemize}
        \item Devised a proof-of-concept (POC) to progressively improve query response in data lakes. Familiarized with \textbf{Apache Calcite} and \textbf{Iceberg}.
        
        \item Improved row-count estimation in \textbf{query planning/optimisation} via accurate statistics observed in prior executions. 
        (LEO, \href{https://www.vldb.org/conf/2001/P019.pdf}{Markl, VLDB 2001}).%
    \end{itemize}
    }

\makework{microsoft}
    {Microsoft}
    {Software Engineer 2}
    {Jun 2016 - Sep 2020}
    {Bengaluru, India}
    {
    \begin{itemize}
        \item Rebuilt workflow manager used for Extract-Transform-Load (\textbf{ETL}) in 100+ pipelines, reducing time-to-deploy from 1h to < 5s. 
        \item Piloted \textbf{Spark} Streaming POC pipeline to compute the statistical significance of A/B tests 3x faster than existing batched method.
        \item Refactored cache config. system in API hosted on \textbf{Azure} using Aspect-Oriented Programming. Decreased config. code 5x, codebase size 300 lines. 
        \item Contributed to teammates' success with detailed input on 40+ design reviews, 100+ \textbf{code reviews}, and live issues on call.
    \end{itemize}
    }

\makework{internmicrosoft}
    {Microsoft}
    {Summer Intern}
    {May 2015 - Jun 2015}
    {Bengaluru, India}
    {
    \begin{itemize}
        \item Analyzed insert \& response times of 3 data stores under stress loads.
        (Azure Data Explorer/\textbf{Kusto}, \textbf{MongoDB}, \textbf{column-store}.)

        \item Concluded Kusto suited the log analysis use-case (response < 5s), column-store the aggregate-based queries (response < 1s). 

        \item Enabled migration from analytical (\textbf{OLAP}) cubes (instant response) to column-store (response < 1s). Cut ETL time from 10 days to 1 hour. 
    \end{itemize}
    }

\makework{gsr}
    {University of California, Irvine}
    {Graduate Student Researcher}
    {Sep 2020 - Sep 2024}
    {Irvine, CA}
    {
    \begin{itemize}
        \item Designed database (DB) plugin that balances latency \& costs,
        allocating \textbf{query-processing} resources to ongoing \& \textbf{ML}-forecast loads.
    
        \item Developed framework for implicit  \textbf{simulator} invocation by DB. 
        Showed ease of analysis by integrating \href{https://www.ready.noaa.gov/HYSPLIT.php}{HYSPLIT} into PostgreSQL. 
        
        \item Created a \textbf{pipeline execution} system for workflows defined as directed acyclic graphs of tasks. (On \href{https://github.com/sriram-rao/rush}{GitHub} as sample.) 
    \end{itemize} 
     } 

\makework{ta}
    {University of California, Irvine}
    {Teaching Assistant}
    {Sep 2020 - Dec 2024}
    {Irvine, CA}
    {
    \begin{itemize}
        \item Rated 4/5 in anonymous feedback from students, with appreciation for database expertise and \textbf{straightforward explanation}. 
    
        \item Collaborated with professors \& TAs on lecture slides, questions, assignments, discussion hours in courses with 200+ students. 
 
    \end{itemize} 
     } 

\makework{drexel}
    {Drexel University}
    {Volunteer Intern}
    {May 2025 - Current}
    {Remote, CA}
    {
    \begin{itemize}
        \item Building an \textbf{iOS app} to intuitively record and export a DBT mood journal. 
    \end{itemize}
    }

\makework{mscs}
    {University of California, Irvine}
    {MS in Computer Science}
    {Sep 2020 - Mar 2025}
    {Irvine, CA}
    {}

\makework{phd}
    {University of California, Irvine}
    {Graduate Work in the PhD Program}
    {Sep 2020 - Sep 2024}
    {Irvine, CA}
    {
    \begin{itemize}
        \item Advised by Prof. Sharad Mehrotra in data management: workload-aware pre-computation.%
    \end{itemize}
    }

\makework{btech}
    {National Institute of Technology, Karnataka}
    {B. Tech. in Computer Engineering}
    {Jul 2012 - Mar 2016}
    {Surathkal, India}
    {}